Orbits

### 2024-03-05 paper/main.tex
Updates from Overleaf

\subsection{Mergers and Orbits}
\subsubsection{Calculation of merger fraction of total sample}
Plot #1: Merger fraction either before or after orbits
\subsubsection{Pulling Orbits}
Orbital data for each pair from the \paircat{} was collected by following each subhalo of the pair both forwards and backwards in time via the \texttt{SUBLINK} algorithm~\citep{RG2015} merger trees.

@@

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\columnwidth]{plots/2_pull-orbits/example-orbit.pdf}
    \caption{}
    % \label{fig:orbitex}
\end{figure*}

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\columnwidth]{plots/1_merged-fraction/mergedfraction.pdf}
    \caption{}
    % \label{fig:merger-frac}
\end{figure*}

>>>>

\subsection{Mergers and Orbits}
\subsubsection{Calculation of merger fraction of total sample}
Plot #1: Merger fraction either before or after orbits
Note that it is very interesting that dwarf pairs in the field have high merger fractions, while the likelihood of merger is very low in more dense environments (add citation).

\subsubsection{Pulling Orbits}
Orbital data for each pair from the \paircat{} was collected by following each subhalo of the pair both forwards and backwards in time via the \texttt{SUBLINK} algorithm~\citep{RG2015} merger trees.

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{plots/bet-on-it/1_fmerge_comp.png}
    \caption{The fraction of pairs that merge before z=0 as a function of the redshift where they were selected via the selection criteria for the \paircat{} from \citet{Chamberlain2024}. At $z>1$, the fraction of selected pairs that merge before $z=0$ is upwards of 80\% for both low mass and high mass isolated pairs. The sharp decline to $F_{\rm merge}$ at $z=0$ is a non-physical feature of the simulation ending at $z=0$, thus unable to follow the pairs after the simulation ends to see what fraction of pairs may have merged.}
    \label{fig:fmerge}
\end{figure}

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\columnwidth]{plots/bet-on-it/}
    \caption{}
    % \label{fig:merger-frac}
\end{figure*}
